---
title: "deep_survival_analysis"
author: "Paidamoyo Chapfuwa"
date: "1/30/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Deep Survival Analysis : EHR
* Item 1
* Item 2
    + Item 2a
    + Item 2b
* Hierachichal Generative Approach
  + survival times and covariates modeled jointly conditional on latent processes
  + records align by failure time rather than entry time
  + Each observation has L layers of latent variables
* (t,c) pairs of positive times and binary censoring status
* Limitations to traditional approches( Cox & Kaplan Meir)
  + EHR highdimensinal and sparse (missing covariates)
  + Traditional methods require aligning all patiets on a synchronizing event(i.e entry to clinical trial)
  + Regression based approaches assume linear function

```{r}
#lamda  scale
# k shape 
# mean = 
# t time to failure
lambda <- 10
t <- seq(0, 20, by=0.1)

weibul <- function(k) {
  return(k/ lambda * (t/ lambda) ^ (k-1)  * exp(-(t/lambda) ^k))
}

plot(t, weibul(10), main = 'weibul distribution',  xlab='t', ylab = '', type='l')
lines(weibul(1), col='blue')
lines(weibul(0.1), col='red')
legend(15, 0.3, legend=c("K=10", "K=1", "K=0.1"), lty = c(1,1,1), col = c('black', 'blue', 'red') )

```

